Data Cleaning

### 2024-11-27 study1/analysis/1_cleaning.qmd
Update 1_cleaning.qmd

df <- read_csv("C:/Users/maisi/OneDrive/Placement/InteroceptionScale/study1/data/rawdata_participants.csv")

# df <- read_csv("C:/Users/emmal/OneDrive - University of Sussex/GitHub/Placement/InteroceptionScale/study1/data/rawdata_participants.csv")

@@

table(df$Country)
```

>>>>

# df <- read_csv("C:/Users/maisi/OneDrive/Placement/InteroceptionScale/study1/data/rawdata_participants.csv")

df <- read_csv("C:/Users/emmal/OneDrive - University of Sussex/GitHub/Placement/InteroceptionScale/study1/data/rawdata_participants.csv")

@@

\## Experiment Enjoyment
